---
title: "Centraldogmabio"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Centraldogmabio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Centraldogmabio)
```

# Introduction

The Centraldogmabio package is a tool for molecular biology and bioinformatics.
It provides a set of of functions with DNA, RNA and amino acid sequences. 
This is the user guide for the package functionalities.
It will also demonstrate how each function can be used individually and in conjunction with others.


# Functions Overview

## Function 1: Codon to Amino Acid Conversion
*'codon_to_aa'*

The first function converts a codon (sequence of 3 nucleotides) to its corresponding amino acid.

## Function 2: DNA to RNA Conversion
*'dna_to_rna'*

The second function transforms a DNA sequence into and RNA sequence by replacing 'T' with 'U'.

## Function 3: Generate Codons from a Genome
*'generate_codon'*

The third function generates codons from a given genom sequence, with an optional starting position.

## Function 4: Generate Random DNA Sequence
*'generate_rand_DNA'*

The fourth function generates a random DNA sequence of a desired length.

## Function 5:Amino Acid Proportion Plot
*'aa_proportions'*

The fifth function creates a bar chart displaying the proportions of amino acids in a given sequence.


# Use Cases

The package can be used in bioinformatics task, such as DNA to protein translation, codon anaysis and sequence visualization.

## Examples

1. Translation Analysis: By converting codons into amino acids protein sequences can be analysed.
2. Sequence Manipulation: Transform DNA to RnA for RNA related analyses.
3. Genomic Analysis: Generating codons for further analysis.
4. Random Sequence Generation: Random DNA sequences for testing of algorithms or for simulation.
5. Visualization: Visualizing the distribution of amino acids in a protein sequence.


# Future Enhancements (other function)

1. Reverse Transcription: Convert RNA back into DNA.
2. Multiple Sequence Alignment: Function for comparing and aligning multople DNA, RNA or protein sequences.
3. Protein Properties: Calculate properties, such as molecular weight, secondary structure prediction, etc..

